Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-01-08 2.background/2.asymptotics.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

We look to derive useful asymptotic approximations for high dimensional problems, and analyze the afore-mentioned procedures in the regime where the dimensionality of the observations diverge.
Throughout this text, we consider triangular arrays of observations as described in Models \eqref{eq:model-additive} and \eqref{eq:model-chisq}, and study the performance of procedures in the signal detection and support recovery tasks when 
\begin{equation*}
  p\to\infty.
\end{equation*}
The criteria for success and failure in support recovery problems under this high-dimensional asymptotic regime are defined as follows.
\begin{definition} \label{def:exact-recovery-success-failure}
We say a sequence of procedures $\mathcal{R} = \mathcal{R}_p$ succeeds asymptotically in the detection problem (and respectively, exact, exact-approximate, approximate-exact, and approximate support recovery problem) if 
\begin{equation} \label{eq:support-recovery-success}
    \mathrm{risk}^{\mathrm{P}}(\mathcal{R}) \to 0, \quad \text{as}\quad p\to\infty,
\end{equation}
where $\mathrm{P}=\mathrm{D}$ (respectively, $\mathrm{E}$, $\mathrm{EA}$, $\mathrm{AE}$, $\mathrm{A}$).

@@

{\bf Signal detection.}
The asymptotic behavior of the statistical risk of signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied in \cite{ingster1998minimax}, where a so-called phase transition phenomena was discovered for sparse additive models \eqref{eq:model-additive} with independent and Gaussian components. 
That is, depending on the signal size and sparsity of the signal $\mu$, the detection risk either vanishes, or has a liminf of 1 when we apply the theoretically optimal \ac{LR} test, as dimensionality of the problem diverges.
The \ac{LR} test, unfortunately, relies on the knowledge of signal sparsity and signal sizes which are often unknown.
The sparsity-and-signal-size-agnostic statistic \ac{HC} was identified to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when errors are dependent \citep{hall2010innovated}.
A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
Notwithstanding the extensive literature on the detection problem, performances of simple statistics such as $L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been sparingly documented. 
We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new reports on the performance of statistics commonly used in practice.

@@

{\bf Exact support recovery.}
There is a wealth of literature on the so-called sparsistency (i.e., $\P[\widehat{S} = S]\to 1$ as $p\to\infty$) problem in the regression context. 
Sparsistency problems were pursued, among many others, by \citet{zhao2006model} and \citet{wasserman2009high} in the high-dimensional regression setting (where the number of samples $n\ll p$), and by \citet*{meinshausen2006high} in graphical models.
Although there have been numerous studies on the sufficient conditions for sparsistency, efforts on necessary conditions have been scarce.
Notable exceptions include \cite{wainwright2009information, wainwright2009sharp} and \cite{comminges2012tight} in regression problems.
We refer readers to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15) for a comprehensive review.

@@

Nevertheless, two important questions remained unanswered.
Namely, precise phase-transition-type results for the exact support recovery risk \eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
% --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
have not been established.
And secondly, performance of commonly used statistical procedures reviewed in Section \ref{sec:statistical-procedures}
in terms of these risk metrics have not been studied.
Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

@@

{\bf Approximate support recovery.}
Performance limits of FDR-controlling procedures in the support recovery problem have been actively studied in recent years.
The asymptotic optimality of the Benjamini-Hochberg procedure
% in the Gaussian scale mixture model 
was analyzed under decision theoretic frameworks in \cite{genovese2002operating, bogdan2011asymptotic, neuvial2012false}, with main focus on location/scale models. 
In particular, these papers show that the statistical risks of the procedures come close to that of the oracle procedures under suitable asymptotic regimes.
Strategies for dealing with multiple testing under general distributional assumptions can be found in, e.g., \cite{efron2004large}, \cite{storey2007optimal}, and \cite{sun2007oracle}.
The two-sided alternative in the additive error model was featured as the primary example in \cite{sun2007oracle}.

In the additive error model \eqref{eq:model-additive} under independent Gaussian errors and one-sided alternatives \eqref{eq:global-test-one-sided},
\cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
The \ac{BH} procedure \cite{benjamini1995controlling}, and the Cand\'es-Barber procedure \cite{barber2015controlling} was identified to be asymptotically optimal. % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
We derive a new phase transitions result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.

@@

{\bf Asymmetric statistical risks.}
Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, none has considered simultaneous family-wise error control and marginal, location-wise power requirements.
As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not been investigated.
As argued in Section \ref{sec:risks}, properties of these asymmetric risks are of important practical concern in applications such as GWAS.
We study the asymptotic behavior of these risks in Chapters \ref{chap:phase-transitions} and \ref{chap:GWAS} of this text.
% ; the results therein have appeared in \cite{gao2019five}.
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

@@

{\bf Chi-square models and GWAS.}
The high-dimensional chi-square model \eqref{eq:model-chisq} seemed to have received little attention in the literature.
While the sparse signal detection problem in the chi-square model has been studied \cite{donoho2004higher}, to the best of our knowledge,  asymptotic limits of the support recovery problems have not been studied.
The chi-squared model and the motivating GWAS application are analyzed in Chapter \ref{chap:GWAS}.
The results obtained therein help us understand the sharp power decay in GWAS that have been long observed \citep{bush2012genome} and recently reviewed and visualized \citep{gao2019upass}.

>>>>

We look to derive useful asymptotic approximations for high-dimensional problems, and analyze the afore-mentioned procedures in the regime where the dimensionality of the observations diverge.
Throughout this text, we consider triangular arrays of observations as described in Models \eqref{eq:model-additive} and \eqref{eq:model-chisq}, and study the performance of various procedures in the signal detection and support recovery tasks when 
\begin{equation*}
  p\to\infty.
\end{equation*}
The criteria for success and failure in support recovery problems under this high-dimensional asymptotic regime are defined as follows.
\begin{definition} \label{def:exact-recovery-success-failure}
We say a sequence of procedures $\mathcal{R} = \mathcal{R}_p$ succeeds asymptotically in the detection problem (and respectively, exact, exact-approximate, approximate-exact, and approximate support recovery problem) if 
\begin{equation} \label{eq:support-recovery-success}
    \mathrm{risk}^{\mathrm{P}}(\mathcal{R}) \to 0, \quad \text{as}\quad p\to\infty,
\end{equation}
where $\mathrm{P}=\mathrm{D}$ (respectively, $\mathrm{E}$, $\mathrm{EA}$, $\mathrm{AE}$, $\mathrm{A}$).

@@

\medskip
{\bf Signal detection.}
\stilian{The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by Yurii Ismailovich Ingster in the context of sparse additive models \eqref{eq:model-additive} with 
independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 
theoretically optimal likelihood ratio (\ac{LR}) test in the high-dimensional asymptotic regime, where the dimension $p$ grows to infinity. Then, under certain parameterization of the size and sparsity of the signal $\mu$, there are only two possibilities: Either ${\rm risk}^D(LR)$ vanishes, as $p\to\infty$, or $\liminf_{p\to\infty} {\rm risk}^D(LR) =1$.
The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered 
by Ingster are described in Chapter \ref{chap:phase-transitions}.}{\fbox{replacing?}
 where a phase transition phenomenon was discovered for 
That is, as $p\to\infty$, depending on the size and sparsity of the signal $\mu$, the detection risk either vanishes, 
or has a liminf of 1 when we apply the theoretically optimal likelihood ratio (\ac{LR}) test. }

The \ac{LR} test, unfortunately, depends  relies on the knowledge of the signal sparsity and signal sizes which are 
not available in practice. The sparsity-and-signal-size-agnostic statistic \ac{HC} in \eqref{eq:HC-statistic} was identified 
to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when the errors are dependent \citep{hall2010innovated}.
A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
Notwithstanding the extensive literature on the detection problem, the performances of simple statistics such as 
$L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been 
sparingly documented.  We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new 
contributions on the performance of several statistics commonly used in practice.

@@

{\bf Exact support recovery.}
There is a wealth of literature on the so-called sparsistency (i.e., $\P[\widehat{S} = S]\to 1$ as $p\to\infty$) problem in the regression context. 
Sparsistency problems were pursued, among many others, by \citet{zhao2006model} and \citet{wasserman2009high} in the high-dimensional regression setting (where the number of samples $n\ll p$), and by \citet*{meinshausen2006high} in graphical models.
Although there have been numerous studies on the sufficient conditions for sparsistency, efforts on necessary conditions have been scarce.
Notable exceptions include \cite{wainwright2009information, wainwright2009sharp} and \cite{comminges2012tight} in regression problems.
We refer the reader to the recent book by \cite{wainwright2019high} (and in particular, the bibliographical sections of Chapters 7 and 15, therein) for a comprehensive review.

@@

Nevertheless, two important questions remained unanswered.
Namely, precise phase-transition-type results for the exact support recovery risk 
\eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
% --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
have not been established.
And secondly, performance of commonly used statistical procedures reviewed in Section \ref{sec:statistical-procedures}
in terms of these risk metrics have not been studied.
\stilian{Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery}, below. Specifically, it turns out that the simple Bonferoni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in 
\eqref{eq:model-additive} under broad classes of error distributions. Furthermore, a phase-transition in the exact support recovery 
problem for thresholding procedures is established under broad dependence conditions on the 
errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}). While the 
optimality of thresholding procedures under dependence remains an open question, in Chapter \ref{sec:optimality}, 
we establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence.  
The landscape of the fundamental statistical limits in support estimation is yet to be fully charted. We conjecture, 
however, that the general concentration of maxima phenomenon will lead to its complete solution under very broad error 
dependence scenarios.  }{
Resolving these two issues, we show in this text that several well-known FWER-controlling procedures --- including Bonferroni's procedure --- are optimal in the additive error model under both one-sided and two-sided alternatives.}
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

@@

{\bf Approximate support recovery.}
The performance limits of FDR-controlling procedures in the support recovery problem have been actively studied in recent years.
The asymptotic optimality of the Benjamini-Hochberg procedure
% in the Gaussian scale mixture model 
was analyzed under decision theoretic frameworks in \cite{genovese2002operating, bogdan2011asymptotic, neuvial2012false}, with main focus on location/scale models. 
In particular, these papers show that the statistical risks of the procedures come close to that of the oracle procedures under suitable asymptotic regimes.
Strategies for dealing with multiple testing under general distributional assumptions can be found in, e.g., \cite{efron2004large}, \cite{storey2007optimal}, and \cite{sun2007oracle}.
The two-sided alternative in the additive error model was featured as the primary example in \cite{sun2007oracle}.

In the additive error model \eqref{eq:model-additive} under independent Gaussian errors and one-sided alternatives \eqref{eq:global-test-one-sided},
\cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
The \ac{BH} procedure \cite{benjamini1995controlling}, and the \stilian{DISCUSS}{Is it Candes-Barber or Barber-Candes?}
Cand\`es-Barber procedure \citep{barber2015controlling} was identified to be asymptotically optimal. % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
We derive a new phase transition result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.

@@

{\bf Asymmetric statistical risks.}
Although weighted sums of false discovery and non-discovery have been studied in the literature mentioned above, \stilian{the case of simultaneous family-wise error control and marginal, location-wise power requirements, has not been previously considered. }{\fbox{Altered, check the wording.}} As a result, asymmetric statistical risks such as \eqref{eq:risk-exact-approx} and \eqref{eq:risk-approx-exact} have not 
been investigated.
As argued in Section \ref{sec:risks}, the properties of these asymmetric risks are of important practical concern in applications such as GWAS.
We study the asymptotic behavior of these risks in Chapters \ref{chap:phase-transitions} and \ref{chap:GWAS} of this text.
% ; the results therein have appeared in \cite{gao2019five}.
% these results have appeared in \cite{gao2018fundamental} and \cite{gao2019five}

@@

{\bf Chi-square models and GWAS.}
The high-dimensional chi-square model \eqref{eq:model-chisq} seemed to have received little attention in the literature.
While the sparse signal detection problem in the chi-square model has been studied \cite{donoho2004higher}, to the best of our knowledge,  asymptotic limits of the support recovery problems have not been studied.
The chi-squared model and the motivating GWAS application are analyzed in Chapter \ref{chap:GWAS}.
\stilian{The results obtained therein help us explain the sharp power decay in GWAS known as the 
{\em steep part of the power curve}.  This empirical fact has long been observed by statistical geneticists \citep{bush2012genome} but so far it had not been mathematically quantified.  \cite{gao2019upass} provide 
further details on the power and design in GWAS as well as an accompanying interactive 
statistical software \citep{gaoUPASS_ShinyApp}.}{\fbox{altered the text, pls check/edit.}}

### 2021-01-08 2.background/2.risks_relations.tex
shortened version
* Implemented my corrections up to Ch.3.1

* Moved the proofs of Ch 3 and the sections on non-AGG models from Ch 4 to the Appendix -- which will become the online supplement.

* We need to cut just 5 pages now...  This can happen by re-distributing some proofs in the text (instead of having them in separate sections) and moving some more proofs from Ch.6 to the Appendix.

* Overall, I don't like the idea to eliminate the proofs from Ch. 3.   I also like having the non-AGG models in the main text, too.  I will think if we can shorten the manuscript in alternative ways....

  O

\begin{lemma} \label{lemma:risk-exact-recovery-probability}
For any sequence of procedures for support recovery $\mathcal{R} = \mathcal{R}_p$, we have, 
%The probability of exact recovery $\P[\widehat{S} = S]$, and risk of exact support recovery $\mathrm{risk}^{\mathrm{E}}$, defined in \eqref{eq:risk-exact}, are related as follows,
\begin{equation} \label{eq:exact-recovery-implies-risk-0}
    \P[\widehat{S} = S] \to 1 \iff \mathrm{risk}^{\mathrm{E}}(\mathcal{R})\to0,
\end{equation}
and
\begin{equation} \label{eq:failure-recovery-implies-risk-1}
    \P[\widehat{S} = S] \to 0 \implies \liminf\mathrm{risk}^{\mathrm{E}}(\mathcal{R})\ge1,
\end{equation}
as $p\to\infty$. Dependence on $p$ was suppressed for notational convenience.
\end{lemma}

@@

Keen readers must have noticed the asymmetry in Relation \eqref{eq:failure-recovery-implies-risk-1} when we discussed the relationship between the exact support recovery risk \eqref{eq:risk-exact} and the probability of exact support recovery \eqref{eq:risk-prob}.

%The converse of \eqref{eq:failure-recovery-implies-risk-1} is not true.
While a trivial procedure that never rejects and a procedure that always rejects both have $\mathrm{risk}^{\mathrm{E}}$ equal to 1, the converse is not true.
For example, it is possible that a procedure selects the true index set $S$ with probability $1/2$, but makes one false inclusion \emph{and} one false omission simultaneously the other half of the time. 
In this case the procedure will have 
$$\mathrm{risk}^{\mathrm{E}} = 1, \quad \text{and} \quad \P[\widehat{S}=S] = 1/2,$$
showing that the converse of Relation \eqref{eq:failure-recovery-implies-risk-1} is in fact false.

The same argument applies to $\mathrm{risk}^{\mathrm{A}}$:
a procedure may select the true index set $S$ with probability $1/2$, but makes enough false inclusions and omissions other half of the time, so that $\mathrm{risk}^{\mathrm{A}}$ is equal to one.
Therefore, although the class of methods with risks equal to or exceeding 1 certainly contains the trivial procedures that we mentioned, they are not necessarily ``useless'' as some researchers have claimed (c.f., \citet{arias2017distribution}, Remark 2).

@@

Turning to the relationship between the probability of exact support recovery \eqref{eq:risk-prob} and Hamming loss \eqref{eq:Hamming-loss}, we point out a natural lower bound of the former using the expectation of the latter,
\begin{equation} \label{eq:Hamming-loss-lower-bound}
    \mathbb{P}[\widehat S = S] 
    \ge 1 - \mathbb{E}[H(\widehat S, S)]
    = 1 - \sum\limits_{i=1}^p\E\left|\mathbbm{1}_{\widehat{S}}(i)- \mathbbm{1}_{S}(i)\right|.
\end{equation}
A key observation in Relation \eqref{eq:Hamming-loss-lower-bound} is that the expected Hamming loss decouples into $p$ terms, and dependence of the estimates $\mathbbm{1}_{\widehat{S}}(i)$ among the $p$ locations no longer plays a role in the sum.
Therefore, studying support recovery problems via the expected Hamming loss is not very informative especially under severe dependence, as the bound \eqref{eq:Hamming-loss-lower-bound} may become {very} loose.
Vanishing Hamming loss is again sufficient, but not necessary for 
$\P[\widehat{S}=S]$ or the exact support recovery risk to fo to zero.
% the probability of exact support recovery --- and hence the exact support recovery risk --- to go to zero.

>>>>

\begin{lemma} \label{lemma:risk-exact-recovery-probability}
For any sequence of procedures for support recovery $\mathcal{R} = \mathcal{R}_p$, we have
%The probability of exact recovery $\P[\widehat{S} = S]$, and risk of exact support recovery $\mathrm{risk}^{\mathrm{E}}$, defined in \eqref{eq:risk-exact}, are related as follows,
\begin{equation} \label{eq:exact-recovery-implies-risk-0}
    \P[\widehat{S} = S] \to 1 \iff \mathrm{risk}^{\mathrm{E}}(\mathcal{R})\to0,
\end{equation}
and
\begin{equation} \label{eq:failure-recovery-implies-risk-1}
    \P[\widehat{S} = S] \to 0 \implies \liminf\mathrm{risk}^{\mathrm{E}}(\mathcal{R})\ge1,
\end{equation}
as $p\to\infty$. Dependence on $p$ and ${\cal R}$ was suppressed for notational convenience.
\end{lemma}

@@

Keen readers must have noticed the asymmetry in Relation \eqref{eq:failure-recovery-implies-risk-1} when we discussed the relationship between the exact support recovery risk \eqref{eq:risk-exact} and the probability of exact support recovery \eqref{eq:risk-prob}.
%
%The converse of \eqref{eq:failure-recovery-implies-risk-1} is not true.
While a trivial procedure that never rejects and a procedure that always rejects both have $\mathrm{risk}^{\mathrm{E}}$ equal to 1, the converse is not true. For example, it is possible that a procedure selects the true index set $S$ with probability $1/2$, but otherwise makes one false inclusion \emph{and} one false omission simultaneously. 
In this case the procedure will have 
$$\mathrm{risk}^{\mathrm{E}} = 1, \quad \text{and} \quad \P[\widehat{S}=S] = 1/2,$$
showing that the converse of Relation \eqref{eq:failure-recovery-implies-risk-1} is in fact false.

The same argument applies to $\mathrm{risk}^{\mathrm{A}}$:
a procedure may select the true index set $S$ with probability $1/2$, but makes enough false inclusions and omissions 
the rest of the time, so that $\mathrm{risk}^{\mathrm{A}}$ is equal to one. Therefore, although the class of methods with 
risks equal to or exceeding 1 certainly contains the trivial procedures that we mentioned, they are not necessarily 
``useless'' as some researchers have claimed \citep[cf.\ Remark 2 in][]{arias2017distribution}.

@@

Turning to the relationship between the probability of exact support recovery \eqref{eq:risk-prob} and Hamming loss \eqref{eq:Hamming-loss}, we point out a natural lower bound of the former using the expectation of the latter,
\begin{equation} \label{eq:Hamming-loss-lower-bound}
    \mathbb{P}[\widehat S = S] 
    \ge 1 - \mathbb{E}[H(\widehat S, S)]
    = 1 - \sum\limits_{i=1}^p\E\left|\mathbbm{1}_{\widehat{S}}(i)- \mathbbm{1}_{S}(i)\right|.
\end{equation}
A key observation in Relation \eqref{eq:Hamming-loss-lower-bound} is that the expected Hamming loss decouples into $p$ terms, and the dependence of the estimates $\mathbbm{1}_{\widehat{S}}(i)$ among the $p$ locations no longer plays any role in the sum.
Therefore, studying support recovery problems via the expected Hamming loss is not very informative especially under severe dependence, as the bound \eqref{eq:Hamming-loss-lower-bound} may become {very} loose.
Vanishing Hamming loss is again sufficient, but not necessary for 
$\P[\widehat{S}=S]$ or the exact support recovery risk to fo to zero.
% the probability of exact support recovery --- and hence the exact support recovery risk --- to go to zero.
